---
title: "FEMMES Data Visualization Workshop"
author: "Revo Tesha & Sibora Seranaj"
date: "2/17/2019"
output: html_document
---

```{r setup, include=FALSE, message=F}
knitr::opts_chunk$set(echo = TRUE)
library(googlesheets)
library(tidyverse)
```

Gmail login info:

email - femmesworkshop2019@gmail.com
password - femmes2019

```{r, include=F}
gs_auth(new_user = TRUE)
```

To see what's in your google drive use gs_ls().

```{r}
quest_res_list <- gs_title("Femmes Questionnaire Responses")
quest_res_df <- for_gs_sheet <- gs_read(quest_res_list)
```

Changing column names:
```{r}
names(quest_res_df) = c("time_stamp", "num_siblings", "fav_color", "height", "shoe_size", "movie_genre", "fav_chocolate", "fav_pet", "fav_season", "fav_num", "reaction", "day_old")
#View(quest_res_df)
```

#### Correlation between shoe number and number of siblings? Too much?

```{r}
ggplot(quest_res_df) + 
  geom_point(aes(x = num_siblings, y = shoe_size)) +
  labs(title = "Relationship Betweenn Shoe Size and Number of Siblings?", x = "Number of Siblings", y = "Shoe Size") + 
  theme()
```

#### Favorite season

```{r}
ggplot(quest_res_df) + 
  geom_bar(aes(x = fav_season)) +
  labs(x = "Favorite Season")
```

#### idea for reaction time 
since kids are recording 5 different reaction time trials, I want to see if there is a trend between the reaction time and the number of trials. For example, I noticed that the first trial I did pretty bad, second one I improved and I kept improving but the last two scores were similar.

```{r}
ggplot(quest_res_df) + 
  geom_bar(aes(x = fav_chocolate)) +
  labs(x = "Favorite Chocolate")
```

#### etc

- gganimate for the reaction times.
- change bar colors e.g. have chocolate types matched with different colors. And the favorite colors one - color by color.
- online shiny course.