---
title: "Writeup"
author: "Revo Tesha"
date: "4/22/2019"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(scales)
library(gridExtra)
library(readxl)
library(grid)
library(grid)
library(viridis)
library(knitr)
library(googlesheets)
library(ggthemes)
# library(gganimate)
# library(ggthemes)
# library(gifski)
# library(png)
```

## Case Study 1: A Better Visualization

```{r child="../Assignment00/Assignment00.Rmd"}

```

## Case Study 2: Femmes 2019

The aim of this assignment was to write code that connects to a survey to
analyse and visualize data that's been provided by the surveyed population.
To do this, we used Rstudios's R markdown to write the analysis and visualization 
code and used google forms to gather data.

We started with creating the google form. This contained eight questions targeted at 
fifth grade girls participating in FEMMES data visualization workshop here at Duke
University. For variability, these questions gathered both categorical and
numeric data. We then created a google sheet to store the responses to these questions. 
In an R markdown file, we implemented the code for analysing and visuazing the survey data.
In the code, we used a package called googlesheets to link the google sheet with 
the R markdown file.

For the visualizions, we included two scatter plots to visualize correlation between two
variables. These two plots were meant to show FEMMES workshop participants the
the difference betweeen correlated and uncorrelated data. We also included two bar
plots to show how one can visualize categorical data and also illustrate 
to students cool things one can do in R, for example changing the color of individual 
bars to virtually any color one prefers. Lastly, we included one animated plot to
show students that it is also possible to animate visualizations in R.

```{r child="../Assignment01/Assignment01.Rmd"}

```

## Case Study 3: CLT Debugging

Debugging CLT_mean shiny applet

The bug:
During applet startup, the error message 'invalid arguments' briefly appear in the
main panel.

Finding the bug:
To find the bug, I first considered the error messages. The fact that the errors
mentioned 'arguments' meant that the cause was coming from how we are passing 
values to the reactive functions that give the outputs. Moreover, since it
is the same error being repeated, I knew that it was a single mistake causing it
and its effect was being propagated throughout the applet. Looking at the
code, the values that are being used repeatedly are those that are being created 
by renderUI and displayed in the UI. So, I read renderUI and uiOutput and found that, 
sometimes when using renderUI and uiOutput to dynamically populate the user controls, 
when the applet launches, the user inputs linked to renderUI are momentarily non-existent.
So, the bug was potentially caused by renderUI inputs.

Fixing the bug:
To fix the bug, I used req() to check validity of all renderUI inputs before using
them. req() check to see if an input is available, and if it is not or if invalid,
it prevents an error message from being displayed. This solution worked.
The only problem is, since req() also completely stops the execution of the code 
proceeding it, using req() stops the graphs from being displayed until the user
clicks on the radio buttons a few times. Other options such as validate() seem to
be causing the same effect and I could not find a clear reason why.


Other changes:
There are a few things I changed in the code. These are as follows:

1. I added wellPanel() to separate user inputs from the additional information
on the user input column. I thought these appear better when separated as thy are 
not related.

2. I removed all the req() for inputs not created inside renderUI. There is 
always a default value for these, so I thought using req() on these was unnecessary.

3. I removed the error message that appears when maximum is less than minimum for
the uniform distribution. Instead of an error message, I made it such that, 
maximum adjusts automatically whenever minimum is made greater than maximum and
minimum adjusts automatically whenever maximum is made smaller than minimum. For
this to work I had to change set the highest possible maximum to 21 instead of 20.

Since it takes a few seconds for this change to happen, an error appears for a few 
seconds after, for example, the user sets a minimum that is greater than the maximum.
To hide this, instead of plotting a graph during this time, I put the message 
'plots reloading ...'. Once the values have been updated, the actual plot displays.

4. The last change I made is re-style the title of the CLT graph so that there is
some space between the title and the frame of the graph.

Update:

To fix the problem caused by req(), I changed all req() calls such that an input
is only required right before it is used. Previously, there was a line that
required all the inputs from renderUI at once. Everytime I deleted some of the inputs
from this line, the code would work without errors. I noticed that, the inputs left
in the line were the same inputs used first in a function that was executing next.
So, instead of requiring all of the inputs together before the function call,
I changed the function to include req() calls everytime an input was about to be
used. So, it turns out that, in this case, req() doesn't prevent graphs from
being drawn.

Additional changes:
1. During meeting, we changed the two sliders for maximum and minimum for the
uniform distributin to have just one slider that gives both maximum and minimum.
This way, there is no need to check if maximum is greater than minimum anymore, so
I remove all the code that does this.

3. I included windowTitle = "CLT for means" to have a shorter window name in the
url.

4. I re-did all the plot with ggplot2 code.
This includes some stylistic changes to texts to match the new plots. I shortened title
of sampling distribution as the information was redundant -- there is a similar 
description right below the graph.

5. I changed the layout of the app to include three tabs. The visulizations are 
now spread over these tabs. This was a suggestion by my supervisor. I also changed 
the ordering of the help text in the user input section to shorten the column so 
it fits the screen. These changes make it easier for the user to see everything in 
one place without having to scroll up and down.

6. For aesthetics, I added background color for the sample distribution plots to match 
the rest of the plots in the app and changed fill colors for the rest of the plots.

Link to final product: [CLT_mean](openintro.shinyapps.io/CLT_mean)

## Case Study 4: Learnr

Link to final product: [learn tutorial](https://revotesha.shinyapps.io/learnr/)

